---
title: "SIM navigator"
description: "This website contains information about the SIM navigator and how to use it"
output: rmdformats::readthedown
---

<style>
  #content {
	max-width: 1400px;
  }
</style>

# Introduction

What is the SIM navigator?

The SIM Navigator was created by a team of students who extracted data from the SIM courses syllabi to create an open dataset of SIM courses. In the SIM programs, students learn the power of data and information to support decision and action.

We hope that the Navigator will help students save time and make ore enlightened decisions about their courses, that it will help faculty

-   Help students get a better sense of the programs and make better de

-   Give quicker and easier access to data related to SIM courses and programs

The SIM navigator provides everyone easier access to data about SIM and its programs, to

-   An open dataset of SIM courses.

-   A set of tools that use the dataset to visualize and explore SIM courses and programs.

-   A zotero library of course readings.

The SIM navigator is a work in progress. If you would like to contribute to its development, please contact [Philippe Mongeon](https://www.dal.ca/faculty/management/school-of-information-management/faculty-staff/faculty/philippe-mongeon.html).

# Explore SIM

The team is currently developing a web application to explore the data. Coming soon.

## Courses

For now, you can already take a quick look at the courses offered at SIM

```{r, echo = FALSE, message=FALSE, warning=FALSE}
library(tidyverse)
library(DT)
courses <- read_delim("data/courses.txt", delim = "\t") %>% 
  select(course_code = '# course_code', title = course_title, type = 'course_type_id', summary) %>% 
  mutate(type = as.character(case_when(type == 1 ~ "Elective",
                          type == 2 ~ "Core",
                          type == 3 ~ "Capstone",
                          type == 4 ~ "Advanced tech")))
  
```

```{r echo = FALSE, message=FALSE}
datatable(courses, filter = 'top', rownames = FALSE, options = list(
  pageLength = 5
))
```

# Dataset {#intro .unnumbered}

## Download {.unnumbered}

The data is structured as a relational database comprising 16 tables. Download a .zip file with all the tab-delimited text files [here](data/sim_navigator_data_202107.zip). You can also download the data as a single Excel file [here](data/sim_navigator_data.xlsx).

The descriptions of all tables and fields can be found in the [documentation] below.

### Archives {.unnumbered}

There are no archived versions of the dataset at this point.

## Documentation {.unnumbered}

This documentation was Generated by MySQL Workbench Model Documentation v1.0.0 - Copyright (c) 2015 Hieu Le.

#### certificates {.unnumbered}

Courses associated with SIM graduation certificates.

+------------------+-------------+-------------------+------------------------------------------------------------+
| Column           | Data type   | Attributes        | Description                                                |
+==================+=============+===================+============================================================+
| `course_code`    | VARCHAR(45) | PRIMARY, Not null | Course code name                                           |
+------------------+-------------+-------------------+------------------------------------------------------------+
| `certificate_id` | INT         | PRIMARY, Not null | ID number associated with each SIM graduation certificate. |
+------------------+-------------+-------------------+------------------------------------------------------------+
| `required`       | TINYINT     |                   | *comment here*                                             |
+------------------+-------------+-------------------+------------------------------------------------------------+

#### competencies {.unnumbered}

List of program competencies.

+-----------------+-------------+-------------------+-------------------------------------+
| Column          | Data type   | Attributes        | Description                         |
+=================+=============+===================+=====================================+
| `competency_id` | SMALLINT    | PRIMARY, Not null | ID number assigned to a competency. |
+-----------------+-------------+-------------------+-------------------------------------+
| `competency`    | VARCHAR(45) |                   | Name of competency.                 |
+-----------------+-------------+-------------------+-------------------------------------+
| `description`   | LONGTEXT    |                   | Description of competency.          |
+-----------------+-------------+-------------------+-------------------------------------+

#### course_types {.unnumbered}

List of course types.

+-------------------+-------------+-------------------+-----------------------------------------+
| Column            | Data type   | Attributes        | Description                             |
+===================+=============+===================+=========================================+
| `coursetype_id`   | VARCHAR(30) | PRIMARY, Not null | ID number assigned to each course type. |
+-------------------+-------------+-------------------+-----------------------------------------+
| `course_type`     | VARCHAR(45) |                   | Course type (elective, core, etc.)      |
+-------------------+-------------+-------------------+-----------------------------------------+
| `type_definition` | LONGTEXT    |                   | Course type description.                |
+-------------------+-------------+-------------------+-----------------------------------------+

#### courses {.unnumbered}

Courses offered at Dalhousie's School of Information Management.

+------------------+--------------+-------------------+------------------------------------------------------------------------------------------------------------------+
| Column           | Data type    | Attributes        | Description                                                                                                      |
+==================+==============+===================+==================================================================================================================+
| `course_code`    | VARCHAR(45)  | PRIMARY, Not null | Code associated with each course.                                                                                |
+------------------+--------------+-------------------+------------------------------------------------------------------------------------------------------------------+
| `course_title`   | VARCHAR(100) |                   | Name of course.                                                                                                  |
+------------------+--------------+-------------------+------------------------------------------------------------------------------------------------------------------+
| `coursetype`     | VARCHAR(45)  |                   | ID number assigned to each course.<br /><br />**foreign key** to column `coursetype_id` on table `course_types`. |
+------------------+--------------+-------------------+------------------------------------------------------------------------------------------------------------------+
| `offered`        | VARCHAR(45)  |                   | Time of year that a course is offered.                                                                           |
+------------------+--------------+-------------------+------------------------------------------------------------------------------------------------------------------+
| `frequency`      | VARCHAR(50)  |                   | How often a course is offered (every year, alternatiing odd years, etc.)                                         |
+------------------+--------------+-------------------+------------------------------------------------------------------------------------------------------------------+
| `summary`        | LONGTEXT     |                   | Description of course.                                                                                           |
+------------------+--------------+-------------------+------------------------------------------------------------------------------------------------------------------+
| `additionalinfo` | VARCHAR(250) |                   | General notes.                                                                                                   |
+------------------+--------------+-------------------+------------------------------------------------------------------------------------------------------------------+

#### courses_assignments {.unnumbered}

List of assignments in each course.

+--------------------+--------------+-------------------+------------------------------------------------------------------------------------------+
| Column             | Data type    | Attributes        | Description                                                                              |
+====================+==============+===================+==========================================================================================+
| `course_code`      | VARCHAR(45)  | PRIMARY, Not null | Course code name.<br /><br />**foreign key** to column `course_code` on table `courses`. |
+--------------------+--------------+-------------------+------------------------------------------------------------------------------------------+
| `assignment_no`    | VARCHAR(10)  | PRIMARY, Not null | Number of assignemnt.                                                                    |
+--------------------+--------------+-------------------+------------------------------------------------------------------------------------------+
| `assignment_title` | VARCHAR(145) |                   | Name of assignment.                                                                      |
+--------------------+--------------+-------------------+------------------------------------------------------------------------------------------+
| `description`      | LONGTEXT     |                   | Assignment description.                                                                  |
+--------------------+--------------+-------------------+------------------------------------------------------------------------------------------+
| `group`            | VARCHAR(5)   |                   | Assignment is either group work or individual. 0 = individual, 1 = group                 |
+--------------------+--------------+-------------------+------------------------------------------------------------------------------------------+
| `weight`           | VARCHAR(45)  |                   | How much the assignment is worth towards your course grade.                              |
+--------------------+--------------+-------------------+------------------------------------------------------------------------------------------+

#### courses_certificates {.unnumbered}

List of certificates and the courses one can take to obtain them.

+----------------------------+--------------+-------------------+--------------------------------------------------------------------------------------------------------------------------+
| Column                     | Data type    | Attributes        | Description                                                                                                              |
+============================+==============+===================+==========================================================================================================================+
| `certificate_name`         | VARCHAR(150) | PRIMARY, Not null | Name of certificate.                                                                                                     |
+----------------------------+--------------+-------------------+--------------------------------------------------------------------------------------------------------------------------+
| `course_code`              | VARCHAR(45)  | PRIMARY, Not null | Code name of course associated with a certificate<br /><br />**foreign key** to column `course_code` on table `courses`. |
+----------------------------+--------------+-------------------+--------------------------------------------------------------------------------------------------------------------------+
| `certificate_requirements` | LONGTEXT     |                   | Description of what is required to receive a specific certificate.                                                       |
+----------------------------+--------------+-------------------+--------------------------------------------------------------------------------------------------------------------------+
| `additional info`          | LONGTEXT     |                   | Notes about certificates and certain courses.                                                                            |
+----------------------------+--------------+-------------------+--------------------------------------------------------------------------------------------------------------------------+

#### courses_competencies_assignments {.unnumbered}

+-----------------+--------------+-------------------+--------------------------------------------------------------------+
| Column          | Data type    | Attributes        | Description                                                        |
+=================+==============+===================+====================================================================+
| `course_code`   | VARCHAR(45)  | PRIMARY, Not null | **foreign key** to column `course_code` on table `courses`.        |
+-----------------+--------------+-------------------+--------------------------------------------------------------------+
| `competency_id` | SMALLINT     | PRIMARY, Not null | **foreign key** to column `competency_id` on table `competencies`. |
+-----------------+--------------+-------------------+--------------------------------------------------------------------+
| `assignment`    | VARCHAR(250) | PRIMARY, Not null |                                                                    |
+-----------------+--------------+-------------------+--------------------------------------------------------------------+

#### courses_crosslist {.unnumbered}

List of courses with an alternate code name.

+---------------------+-------------+-------------------+----------------------------------------------------------------------------------------------+
| Column              | Data type   | Attributes        | Description                                                                                  |
+=====================+=============+===================+==============================================================================================+
| `course_code`       | VARCHAR(45) | PRIMARY, Not null | Code name for course.<br /><br />**foreign key** to column `course_code` on table `courses`. |
+---------------------+-------------+-------------------+----------------------------------------------------------------------------------------------+
| `other_course_code` | VARCHAR(15) | PRIMARY, Not null | Alternate code name for a course.                                                            |
+---------------------+-------------+-------------------+----------------------------------------------------------------------------------------------+

#### courses_instructor {.unnumbered}

List of instructors and the courses they teach.

+-----------------+-------------+-------------------+------------------------------------------------------------------------------------------------------------------+
| Column          | Data type   | Attributes        | Description                                                                                                      |
+=================+=============+===================+==================================================================================================================+
| `instructor_id` | VARCHAR(10) | PRIMARY, Not null | ID number assigned to an instructor.<br /><br />**foreign key** to column `instructor_id` on table `instructor`. |
+-----------------+-------------+-------------------+------------------------------------------------------------------------------------------------------------------+
| `course_code`   | VARCHAR(45) | PRIMARY, Not null | Course code name.<br /><br />**foreign key** to column `course_code` on table `courses`.                         |
+-----------------+-------------+-------------------+------------------------------------------------------------------------------------------------------------------+

#### courses_learning_objectives {.unnumbered}

List of learning objectives associated with each course.

+-----------------------+--------------+-------------------+---------------------------------------------------------------------------------------------+
| Column                | Data type    | Attributes        | Description                                                                                 |
+=======================+==============+===================+=============================================================================================+
| `course_code`         | VARCHAR(45)  | PRIMARY, Not null | Code name of course.<br /><br />**foreign key** to column `course_code` on table `courses`. |
+-----------------------+--------------+-------------------+---------------------------------------------------------------------------------------------+
| `learning_objectives` | VARCHAR(250) | PRIMARY, Not null | Learning objective associated with a course.                                                |
+-----------------------+--------------+-------------------+---------------------------------------------------------------------------------------------+

#### courses_prerequisites {.unnumbered}

List of courses and their pre-requisites courses.

+----------------+--------------+-------------------+------------------------------------------------------------------------------------------------+
| Column         | Data type    | Attributes        | Description                                                                                    |
+================+==============+===================+================================================================================================+
| `course_code`  | VARCHAR(45)  | PRIMARY, Not null | Code name for a course.<br /><br />**foreign key** to column `course_code` on table `courses`. |
+----------------+--------------+-------------------+------------------------------------------------------------------------------------------------+
| `prerequisite` | VARCHAR(200) | PRIMARY, Not null | Previously taken course(s) required to take a specific class.                                  |
+----------------+--------------+-------------------+------------------------------------------------------------------------------------------------+

#### courses_programs {.unnumbered}

List of courses and the SIM program they are associated with.

+---------------+-------------+-------------------+----------------------------------------------------------------------------------------------------------------------+
| Column        | Data type   | Attributes        | Description                                                                                                          |
+===============+=============+===================+======================================================================================================================+
| `course_code` | VARCHAR(45) | PRIMARY, Not null | Code name of a course.<br /><br />**foreign key** to column `course_code` on table `courses`.                        |
+---------------+-------------+-------------------+----------------------------------------------------------------------------------------------------------------------+
| `program_id`  | VARCHAR(45) | PRIMARY, Not null | Program a course is associated with (ex. MI).<br /><br />**foreign key** to column `program_id` on table `programs`. |
+---------------+-------------+-------------------+----------------------------------------------------------------------------------------------------------------------+

#### courses_technologies {.unnumbered}

List of tecnologies each course uses.

+-----------------+-------------+-------------------+------------------------------------------------------------------------------------------------------------+
| Column          | Data type   | Attributes        | Description                                                                                                |
+=================+=============+===================+============================================================================================================+
| `course_code`   | VARCHAR(45) | PRIMARY, Not null | Code name of course.<br /><br />**foreign key** to column `course_code` on table `courses`.                |
+-----------------+-------------+-------------------+------------------------------------------------------------------------------------------------------------+
| `technology_id` | SMALLINT    | PRIMARY, Not null | Technology used in a course.<br /><br />**foreign key** to column `technology_id` on table `technologies`. |
+-----------------+-------------+-------------------+------------------------------------------------------------------------------------------------------------+

#### instructors {.unnumbered}

List of SIM instructors.

+-----------------+-------------+-------------------+------------------------------------------------------+
| Column          | Data type   | Attributes        | Description                                          |
+=================+=============+===================+======================================================+
| `instructor_id` | VARCHAR(10) | PRIMARY, Not null | ID number assigned to an instructor.                 |
+-----------------+-------------+-------------------+------------------------------------------------------+
| `first_name`    | VARCHAR(45) |                   | Instructor's first name.                             |
+-----------------+-------------+-------------------+------------------------------------------------------+
| `last_name`     | VARCHAR(45) |                   | Instructor's last name.                              |
+-----------------+-------------+-------------------+------------------------------------------------------+
| `status`        | LONGTEXT    |                   | Instructor status (ex. Lecturer, Adjunct Professor). |
+-----------------+-------------+-------------------+------------------------------------------------------+
| `email`         | VARCHAR(45) |                   | Email address of instructor.                         |
+-----------------+-------------+-------------------+------------------------------------------------------+

#### programs {.unnumbered}

List of programs offered by Dalhousie's School of Information Management.

| Column       | Data type   | Attributes        | Description                      |
|--------------|-------------|-------------------|----------------------------------|
| `program_id` | VARCHAR(45) | PRIMARY, Not null | ID number assigned to a program. |
| `name`       | VARCHAR(45) |                   | Name of program.                 |

#### technologies {.unnumbered}

List of possible technologies used in SIM courses.

+-----------------+--------------+------------------------------------+-------------------------------------+
| Column          | Data type    | Attributes                         | Description                         |
+=================+==============+====================================+=====================================+
| `technology_id` | SMALLINT     | PRIMARY, Auto increments, Not null | ID number assigned to a technology. |
+-----------------+--------------+------------------------------------+-------------------------------------+
| `technology`    | VARCHAR(255) |                                    | Name of technology.                 |
+-----------------+--------------+------------------------------------+-------------------------------------+

# Zotero Library {.unnumbered}

A public Zotero Library containing all the School of Information Management course readings can be found [here](https://www.zotero.org/groups/4286370/sim_navigator/library){.uri}.

You can also download the entire Zotero library in BibTeX format [here](zotero/sim_library_ref_only.bib) (references only).

# Contributors {.unnumbered}

Thank you to SIM students who helped create the SIM navigator:

-   Theresa Boulos

-   Ratna Dhaliwal

-   Vinson Li

-   Molly McDougall

-   Poppy Riddle
